Predictive 3D modelling of free oblique cutting with an Artificial Neural Network (ANN)-based material constitutive model and experimental validation over a wide range of conditions

### 2023-11-22 Article.tex
Version soumise à EAAI
Journal et titre mis à jour

\journal{CIRP Journal of Manufacturing Science and Technology}

@@

\title{Predictive 3D modelling of free oblique cutting with an ANN-based material constitutive model and experimental validation over a wide range of conditions}

>>>>

\journal{Engineering Applications of Artificial Intelligence}

@@

\title{Predictive 3D modelling of free oblique cutting with an Artificial Neural Network (ANN)-based material constitutive model and experimental validation over a wide range of conditions}
